---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `eyeris`: create and run flexible and reproducible pupillometry preprocessing pipelines in R

<!-- badges: start -->
<a href="LICENSE.md" alt="MIT License">
  <img src="https://badgen.net/static/license/MIT/blue?icon=github" />
</a>
<a href="https://github.com/shawntschwartz/eyeris/actions/workflows/build.yml/badge.svg" alt="R Package Build Status">
  <img src="https://github.com/shawntschwartz/eyeris/actions/workflows/build.yml/badge.svg" />
</a>
<a href="https://github.com/shawntschwartz/eyeris/actions/workflows/linter.yml/badge.svg" alt="R Package Linter Status">
  <img src="https://github.com/shawntschwartz/eyeris/actions/workflows/linter.yml/badge.svg" />
</a>
<!-- badges: end -->

<!-- The goal of eyeris is to ... -->

## Installation

You can install the development version of eyeris from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("shawntschwartz/eyeris")
```

or

``` r
# install.packages("devtools")
devtools::install_github("shawntschwartz/eyeris")
```

## Example

### the `glassbox()` "prescription" function

This is a basic example of how to use `eyeris` out of the box with our very
*opinionated* set of steps and parameters that one should start out with when
preprocessing pupillometry data. Critically, this is a "glassbox" -- as opposed
to a "blackbox" -- since each step and parameter implemented herein is fully
open and accessible to you. We designed each pipeline step / function to be like
legos -- they are intentionally and carefully designed in a way that allows you
to flexibly construct and compare different pipelines.

We hope you enjoy! -shawn

```{r example}
library(eyeris)

set.seed(1)

demo_data <- system.file("extdata", "assocret.asc", package = "eyeris")

eyeris_preproc <- glassbox(demo_data) # also try setting `interactive` to TRUE
```

```{r plot, echo = FALSE, fig.width=3, fig.height=3}
plot(eyeris_preproc)
```

# Comments, suggestions, questions, issues

> [!IMPORTANT]  
> Please use the issues tab (https://github.com/shawntschwartz/eyeris/issues) to make note of any bugs, comments, suggestions, feedback, etc... all are welcomed and appreciated, thanks!
